---
title       : Coursera Data Products Pitch
subtitle    : Quandl Explorer
author      : steveL
job         : student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## The motivation {.build}

>- I don't know if you remember the lecture in this course a few lessons ago that used an example data-set pulled down from Quandl?
>- I saw it and thought, hey, that looks pretty cool, wonder when I can find an excuse to play around with that?
>- Well, this is my excuse.

---

## The Product

>- Quandl is an API that lets you pull data sets into R like this 

```{r, eval=FALSE}
    coolData<-Quandl(datacode)
```

>- They're mainly time series data, I'm not sure why, but there's a nice coverage of topics. Lots of financial data, but also heath and social-demographics stuff.
>- Maybe you had the same thought I did on seeing that code fragment: "Cool, but how do I know what 'datacode' to use?"
>- There's a Quandl website, but I didn't find it super search-friendly.

---

## The Product

>- A much better way to search is to use the Quandl search function:

```{r, eval=FALSE}
        searchresults<-Quandl.search(searchtext)
```

>- This returns a list of 'results', where each result is a list with entries "name" "code" "description"  "frequency" and "column_names"

>- The Shiny app I built for this project is just a GUI for this search function.

>- It allows you to enter a search string, puts the 'name' of each result into a dropdown menu, and on selecting the menu, displays the 'description' and attempts to plot the data.

---

## Known issues

>- It's not really very practical, but I had hours of fun typing in random words and looking at the line plots associated with them.
>- I'm pretty easily amused.
>- There are some rough edges still.
>- It doesn't degrade gracefully with a bunch of common error conditions.
>- But the flaw that really bothers me is the way the plots assume the date/time info is in the first variable, and only plot one other variable. Many of the Quandl datasets carry many variables.

---

## Thanks for your time

Anyway, cheers for looking this over. I'll look forward to your comments!